---
title: "Mathematics Summer Projects: Week 1"
author: "Charlotte Hull"
format: html
editor: visual
---

## Week 1

### Mathematical expressions in LaTeX

The Greek alphabet, for example, can be represented with [LaTeX](https://www.latex-project.org/).

Characters such as $\theta$ , $\rho$ , $\beta$ and $\pi$ can be used.

It can also be used to represent any equations or mathematical symbols required, as seen below:

$$
\int 2x \,dx = x^2 +C
$$

You can also use an integral with limits. Similar syntax can be used to display sums, products, limits, etc.

$$
\int_{0}^{\infty} x^2 \,dx
$$

### R & Python chunks

Quarto can also support R and python code.

This outputs the sum, using R.

```{r}
1+1
```

This summarizes the information within the dataset cars

```{r}
summary(cars)
```

You can also remove the `echo` so that the R code is not displayed, only the output. Here is the same data, without the code.

```{r}
#| echo: FALSE
summary(cars)
```

You can also run python code using the reticulate package

```{python}
4+5
```

Below is the same plot, the first using the ggplot2 package (with some formatting), and the second using the standard plotting function in R.

```{r}
library(ggplot2)

ggplot(cars, aes(x=speed, y=dist))+
  geom_point(color = "#eb4034", size = 5)   
```

```{r}
plot(cars)
```

Below is the same plot, the first using python code, and the second using R, using the music.csv data

```{python}
import pandas as pd 

df=pd.read_csv('music.csv')
df.plot.scatter(x='Year',y='Average_Rating', s=2)
```

```{r}
library(ggplot2)
df = read.csv('music.csv')
ggplot(df, aes(x= Year, y= Average_Rating))+
  geom_point(color = "#000000", size = 1)
```
